Lessons Learned about JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2020-03-12 ms.tex
spectral and spatial covariances

@@

We have demonstrated that row-by-row and amplifier-by-amplifier median subtraction can substantially reduce the read noise for a correlated double sample subtraction from 23,500 DN to 2,900 DN.
Therefore, the corrected read noise per integration should be:
\begin{equation}\label{bestRNCorrection}
RN_{ap,70,75,100} = \frac{4,100 DN}{ \sqrt{N_{frames}}}
\end{equation}
\textcolor{red}{\bf This is for the ALONG detector.
Update for the A3 detector}
For the same $K$=8.5 magnitude star observed in full frame imaging WEAK LENS +8 imaging mode, the read noise per integration should be 1,700 DN.
Fortunately, this is now a small fraction of the photon uncertainty of 9,100 DN and only amounts to an increase in noise over the 51 ppm photon by 9 ppm per integration.

@@

>>>>

\subsubsection{Empirical Covariance Matrix}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.7\columnwidth]{spec_spatial_cov.pdf}
\caption{The read noise is strongly correlated in the spectral direction (diagnoal boxes) and somewhat correlated in the spatial direction (off diagonal region).}\label{fig:covSpeSpatial}
\end{figure}

@@

We have demonstrated that row-by-row and amplifier-by-amplifier median subtraction can substantially reduce the read noise for a correlated double sample subtraction from 23,500 DN to 2,900 DN.
Therefore, the corrected read noise per integration should be:
\begin{equation}\label{eq:bestRNCorrection}
RN_{ap,70,75,100} = \frac{4,100 DN}{ \sqrt{N_{frames}}}
\end{equation}
\textcolor{red}{\bf This is for the ALONG detector.
Update for the A3 detector}
For the same $K$=8.5 magnitude star observed in full frame imaging WEAK LENS +8 imaging mode, the read noise per integration should be 1,700 DN.
Fortunately, this is now a small fraction of the photon uncertainty of 9,100 DN and only amounts to an increase in noise over the 51 ppm photon by 9 ppm per integration.

@@

\subsubsection{Impact to Grism Time series}
We consider a 0.17$\mu$m-wide wavelength bin and 20 pixel aperture diameter as a test case for how badly it will impact spectroscopic features that are 0.17$\mu$m wide.
In this case, we assume row-by-row subtraction is performed and that the CDS noise from the OTIS ground-based test is representative of flight.
Then, the equivalent grism aperture noise to equation \ref{eq:bestRNCorrection} is
\begin{equation}
RN_{grism,0.17\mu\mathrm{m}} = \frac{5,130 DN}{ \sqrt{N_{frames}}}.
\end{equation}
For the grism aperture
